---
title: "ASDA Project 2"
author: "Graham Davies"
date: "27/10/2021"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Libraries
```{r}
library(dplyr)
library(tidyr)

library(sf)
library(spatstat)
library(spatstat.data)
library(ggplot2)
library(sp)
library(animation)
library(plotrix)

library(tmap)
library(spdep)
library(maptools)




# if (!require("pacman")) install.packages("pacman")
# pacman::p_load(dplyr, kohonen, datasets, grid, tidyverse, ggplot2, lubridate, arules,plyr)
# pacman::p_load(here, data.table, purrrlyr,
#                tidyverse,  simplevis, gt, gtsummary, flextable, SmartEDA, DataExplorer, DT, expss, ggcal, vtree, inspectdf,
#                lubridate, janitor, forcats, fastDummies, units,
#                tsibble, feasts, fable,
#                sf, raster, mapproj, tmap, tmaptools, mapdeck,leaflet, leafgl, rgeoda, osmplotr, osmdata,
#                exactextractr, geomerge, hereR, ggmap,
#                kableExtra, knitr,
#                colourvalues, viridis,
#                readxl, rio, fst,
#                tictoc, beepr,
#                ggfortify, gganimate,
#                grateful)
```

Data Preparation and cleaning
```{r}
rm(list = ls())
load("airbnbdata.RData")

#class(cpt_listings_in_sf)

cpt_listings_in <- cpt_listings_in %>%
  mutate(price_clean = price,
         price_clean = as.numeric(str_remove_all(price_clean, "\\$|,")),
         bathroomst  = replace(bathroomst,bathroomst == "Half-bath", 0.5),
         bathroomst  = replace(bathroomst,bathroomst == "Shared half-bath", 0.5),
         bathroomst  = replace(bathroomst,bathroomst == "Private half-bath", 0.5),
         bathroomst  = str_remove_all(bathroomst, "private |shared |s"),
         bathrooms   = as.numeric(str_remove_all(bathroomst, " bath")),
         haccrclean  = haccr,
         haccrclean  = as.numeric(str_remove_all(haccr, "\\%"))) %>%
  mutate(across(where(is.logical), as.character)) %>%
  mutate(pricePH = as.numeric(pclean/accommodates))
```

Dummy's
```{r}
cpt_listings_in = cpt_listings_in%>%mutate(var = 1) %>%
  spread(rtype, var, fill = 0, sep = "_") %>%
  left_join(cpt_listings_in) %>%
  dplyr::select(everything())

cpt_listings_in = cpt_listings_in%>%mutate(var = 1) %>%
  spread(ptype, var, fill = 0, sep = "_") %>%
  left_join(cpt_listings_in) %>%
  dplyr::select(everything())

#instant bookable
cpt_listings_in = cpt_listings_in%>%mutate(var = 1) %>%
  spread(insbook, var, fill = 0, sep = "_") %>%
  left_join(cpt_listings_in) %>%
  dplyr::select(everything())

#fully booked
cpt_listings_in = cpt_listings_in%>%mutate(var = 1) %>%
  spread(fbooked, var, fill = 0, sep = "_") %>%
  left_join(cpt_listings_in) %>%
  dplyr::select(everything())

#superhost
cpt_listings_in = cpt_listings_in%>%mutate(var = 1) %>%
  spread(hsuperhost, var, fill = 0, sep = "_") %>%
  left_join(cpt_listings_in) %>%
  dplyr::select(everything())
```

#EDA
```{r}
attach(cpt_listings_in)

#univariate price
png("uniPrice.png")
hist(pclean, ylab = "No. listings", col = "4", main = "Histogram of price", breaks = 50)
dev.off()

png("uniPriceCut.png")
hist(pclean[pclean < 3000], ylab = "No. listings", col = "4", main = "Histogram of price < 3000", breaks = 20)
dev.off()



#bedroom
png("bedRoom2.png")
cpt_listings_in %>% ggplot(mapping = aes(x = bedrooms, y = log(pclean))) + geom_point() + xlab("Bedrooms") + ylab("Log(Price)")
dev.off()

png("bathRoom2.png")
cpt_listings_in %>% ggplot(mapping = aes(x = bathrooms, y = log(pclean))) + geom_point() + xlab("Bathrooms") + ylab("Log(Price)")
dev.off()

png("pricePerHead.png")
cpt_listings_in %>% ggplot(mapping = aes(x = 1:length(pricePH), y = sort(pricePH))) + geom_point() + xlab("Observations") + ylab("Price")
dev.off()



#room type
png("pieRoomType.png")
pie(table(rtype), main = "Pie chart of Room types") 
dev.off()

#Property type
png("piePropType.png")
pie(table(ptype), main = "Pie chart of Property types", border = T) #don't use
dev.off()




#Next compare host
png("barSuperHost.png")
barplot(table(hsuperhost), main = "Barplot of Superhost", xlab = "Whether the host is a super host", col = "4") #only 16 NA values
dev.off()

png("barActRate.png")
barplot(table(haccrclean), main = "Barplot of Host acceptance rate", xlab = "That rate at which a host accepts booking requests (%)", col = "4")
dev.off()



#book variables
png("barInsBook.png")
barplot(table(insbook), main = "Barplot of Instant bookable", xlab = "Whether the listing is instantly bookable", col = "4", ylim  = c(0, 10000))
dev.off()

png("barFullBook.png")
barplot(table(fbooked), main = "Barplot of Fully booked", xlab = "Whether the listing is fully booked", col = "4")
dev.off()


#review variables
png("cleanlinessRating.png")
hist(rscl, main = "Histogram of Review Score cleanliness", xlab = "Rating out of 5", col = "4", n = 25)
dev.off()

png("reviewScore.png")
hist(rsr, main = "Histogram of Review Score rating", xlab = "Rating out of 5", col = "4", n = 25)
dev.off()

png("reviewScoreValue.png")
hist(rsval, main = "Histogram of Review Score value", xlab = "Rating out of 5", col = "4", n = 25)
dev.off()

png("reviewCommunication.png")
hist(rscom, main = "Histogram of Review Score communication", xlab = "Rating out of 5", col = "4", n = 25)
dev.off()

png("reviewLoc.png")
hist(rsloc, main = "Histogram of Review Score location", xlab = "Rating out of 5", col = "4", n = 25)
dev.off()

png("reviewPM.png")
hist(log(rpmonth), main = "Histogram of Reviews per month", xlab = "Rating out of 5", col = "4", n = 25)
dev.off()


#latitude and longitude. Could have impact as Clifton/coastal wards may be more pricy
png("mapWard.png", width = 750, height = 450)
cpt_listings_in %>%ggplot(mapping = aes(x = latitude, y = longitude, colour = factor(WARDNO))) + geom_point() + guides(fill=guide_legend(title="New Legend Title"))
dev.off()
detach(cpt_listings_in)
```


```{r}
library(sp)
# prepare coordinates, data, and proj4string
coords <- cpt_listings_in[,c(31,32)]   # coordinates
dataSP <- as.data.frame(cpt_listings_in)         # data
crs    <- CRS("+init=epsg:28992") # proj4string of coords

# make the SpatialPointsDataFrame object
spdf <- SpatialPointsDataFrame(coords      = coords,
                               data        = dataSP, 
                               proj4string = crs)
```

#SPPA
```{r}
library(sf)
library(spatstat)
library(spatstat.data)
library(ggplot2)
library(sp)
library(animation)
library(plotrix)

library(maps)
library(ggmap)

cpt_areas_in <- cpt_areas_in[-110, ]
cpt_areas_in_df <- cpt_areas_in_df[-110, ]
cpt_areas_in_sf <- cpt_areas_in_sf[-110, ]
```


```{r}
cptSP <- as(cpt_listings_in_sf, Class = "Spatial")
w62 <-  cptSP[which(cptSP$WARDNO == 62),] #514
w84 <-  cptSP[which(cptSP$WARDNO == 84),] #301
```


Mapping Cape Town Wards
```{r}
#Ward 62
ctLongLat62 <-c(bbox(w62)[1,1], bbox(w62)[2,1], bbox(w62)[1,2],bbox(w62)[2,2])
ctLongLat62

#cpt_areas_in$geometry[which(cpt_areas_in$neighbourhood == "Ward 62")]

ctLongLat62<- c(18.4, -34.05,  18.475, -33.965)
map62 <- get_map(location = ctLongLat62)

mapPoints62 <- ggmap(map62) + 
  geom_point(aes(x = w62@coords[,1], y = w62@coords[,2]),
             data = w62@data, alpha = 1,size=.5, color = "red") + 
  labs(title="Spatial location of Ward 62",
       y="Latitude",x="Longtitude" ) 
#png("googleWard62.png")
mapPoints62
#dev.off()


#Ward 84
ctLongLat84 <-c(bbox(w84)[1,1], bbox(w84)[2,1], bbox(w84)[1,2],bbox(w84)[2,2])
ctLongLat84

ctLongLat84<-c(18.835, -34.13,  18.95, -34.025)
map84 <- get_map(location = ctLongLat84)

mapPoints84 <- ggmap(map84) + 
  geom_point(aes(x = w84@coords[,1], y = w84@coords[,2]),
             data = w84@data, alpha = 1,size=.5, color = "blue") +  
  labs(title="Spatial location of Ward 84",
       y="Latitude",x="Longtitude" ) 
#png("googleWard84.png")
mapPoints84
#dev.off()



#Google maps plot
ctLongLat <-c(bbox(cptSP)[1,1], bbox(cptSP)[2,1], bbox(cptSP)[1,2],bbox(cptSP)[2,2])
ctLongLat

ctLongLat<-c(18.30745, -34.2,  19.00467, -33.85)
map <- get_map(location = ctLongLat)

mapPoints <- ggmap(map) + 
  geom_point(aes(x = w62@coords[,1], y = w62@coords[,2]),
             data = w62@data, alpha = 1,size=.5, color = "red") + 
  geom_point(aes(x = w84@coords[,1], y = w84@coords[,2]),
             data = w84@data, alpha = 1,size=.5, color = "blue") + 
  labs(title="Spatial location of Wards",
       y="Latitude",x="Longtitude" ) 

#png("googleWard.png")
mapPoints
#dev.off()
```

Ward divisions
```{r}
library(ggplot2)
plot2 = ggplot() + 
  geom_sf(data = cpt_areas_in_sf, size = .8, color = "black") + 
  ggtitle("Location of Cape Town Wards") + 
  coord_sf(xlim = c(18.34, 18.91), ylim = c(-34.19, -33.51262)) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_rect(colour = "black", size=1, fill=NA))
plot2
```


#Quadrat analysis
```{r}
#cptPPP <- ppp(x = cpt_listings_in$latitude, y = cpt_listings_in$longitude, window=as.owin(cpt_areas_in_sf$geometry[which(cpt_areas_in_sf$neighbourhood == "Ward 62")][[1]]))



#62 ppp
ppp62 <- as(w62, Class = "SpatialPoints")
ppp62 <- elide(ppp62, scale = NULL, unitsq = TRUE) #scaled
ppp62 <- as(ppp62, Class = "ppp")
Window(ppp62) <- as.owin(cpt_areas_in_sf$geometry[which(cpt_areas_in_sf$neighbourhood == "Ward 62")][[1]])
plot(ppp62)

#84 ppp
ppp84 <- as(w84, Class = "SpatialPoints")
ppp84 <- elide(ppp84, scale = NULL, unitsq = TRUE) #scaled
ppp84 <- as(ppp84, Class = "ppp")
Window(ppp84) <- as.owin(cpt_areas_in_sf$geometry[which(cpt_areas_in_sf$neighbourhood == "Ward 84")][[1]])
ppp84 <- as(ppp84, Class = "ppp")

plot(ppp84)
```


Ward 62 Quadrat
```{r}
dimen = 5

Q62 = quadratcount(ppp62, nx=dimen, ny=dimen)
png("pointCount62.png")
plot(ppp62, pch = 20, main  = "Observed point counts")
plot(Q62, add=TRUE, col="red", cex=1.5, lty=2)
dev.off()



#Plotting density
# Plot the density
cl <-  interp.colours(c("lightyellow", "orange" ,"red"), 20)

png("intensity62.png")
plot(intensity(Q62, image=TRUE), las=1, col=cl, main= "Intensity plot")
plot(ppp62, pch=20, cex=0.6, col="black", add=TRUE)  # Add points
dev.off()


#Quadrat test
Qtest62 = quadrat.test(ppp62, dimen, dimen)
```


Ward 84 Quadrat
```{r}
dimen = 5

png("pointCount84.png")
Q84 = quadratcount(ppp84, nx=dimen, ny=dimen)
plot(ppp84, pch = 20, main  = "Observed point counts")
plot(Q84, add=TRUE, col="red", cex=1.5, lty=2)
dev.off()


#Plotting density
# Plot the density
cl <-  interp.colours(c("lightyellow", "orange" ,"red"), 20)

png("intensity84.png")
plot(intensity(Q84, image=TRUE), las=1, col=cl, main= "Intensity plot")
plot(ppp84, pch=20, cex=0.6, col="black", add=TRUE)  # Add points
dev.off()

#Quadrat test
Qtest84 = quadrat.test(ppp84, dimen, dimen)
```


Kernel density smoothing
Ward 62
```{r}
bw.diggle(ppp62)
den62 <- density(ppp62, sigma = 0.005 ) #.15 #.2  #.3

png("kernal62.png")
plot(den62, main = "Ward 62")
plot(ppp62, add=TRUE)
contour(den62, add=TRUE)
dev.off()
```

Ward 84
```{r}
bw.diggle(ppp84)
den84 <- density(ppp84, sigma = 0.008 ) #0.01 #0.009

png("kernal84.png")
plot(den84, main = "Ward 84")
plot(ppp84, add=TRUE)
contour(den84, add=TRUE)
dev.off()
```


e2e distance
```{r}
#e2e_62 = nndist(ppp62) #nearest neighbour diatance
dm62 <- as.matrix(pairdist(ppp62))#pairwise distance matrix

diag(dm62) <- NA
wdmin62 <- apply(dm62, 1, which.min)

dmin62 <- nndist(ppp62) #use this 

plot(ppp62) # create plot
xy = cbind(ppp62$x, ppp62$y) # get coords

ord <- rev(order(dmin62))
far25 <- ord[1:514] #no. observations
neighbors <- wdmin62[far25]
points(xy[far25, ], col='blue', pch=20)
points(xy[neighbors, ], col='red')

# drawing the lines, easiest via a loop
for (i in far25) 
{
    lines(rbind(xy[i, ], xy[wdmin62[i], ]), col='red')
}


#p2e
#create random points
randompoints = matrix(runif(257),ncol=2)


plot(ppp62)
points(randompoints, col = "blue", pch=3) #plot of the random points


# p2e_distances_cluster = NULL
# mins_cluster = NULL
# 
# for(i in 1:dim(randompoints)[1])
# {
#   dist1 = matrix(pairdist(rbind(randompoints[i,],xy)),514)
#   
#   p2e_distances_cluster = c(p2e_distances_cluster,min(dist1[2:514,1]))
#   mins_cluster = c(mins_cluster,which.min(dist1[2:514,1]))
# }
# 
# 
# plot(pp_cluster)
# ord <- rev(order(p2e_distances_cluster))
# far25 <- 1:dim(randompoints)[1]
# neighbors <- mins_cluster
# points(randompoints, col='red', pch=4)
# points(xy[mins_cluster, ], col='blue', pch=2)
# # drawing the lines, easiest via a loop
# for (i in far25) {
#   lines(rbind(xy[mins_cluster[i], ], randompoints[i, ]), col='red')
# }

```

```{r}
dm84 <- as.matrix(pairdist(ppp84)) #paired distance matrix

diag(dm84) <- NA
wdmin84 <- apply(dm84, 1, which.min)

dmin84 <- nndist(ppp84) #use this 

plot(ppp84) # create plot
xy = cbind(ppp84$x, ppp84$y) # get coords

ord <- rev(order(dmin84))
far25 <- ord[1:301] #no. observations
neighbors <- wdmin84[far25]
points(xy[far25, ], col='blue', pch=20)
points(xy[neighbors, ], col='red')

# drawing the lines, easiest via a loop
for (i in far25) 
{
    lines(rbind(xy[i, ], xy[wdmin84[i], ]), col='red')
}
```

p2e distance
```{r}
p2e_distances_cluster = NULL
mins_cluster = NULL
xy_cluster = cbind(pp_cluster$x, pp_cluster$y)

for(i in 1:dim(randompoints)[1])
{
  dist1 = matrix(pairdist(rbind(randompoints[i,],xy_cluster)),41)
  
  p2e_distances_cluster = c(p2e_distances_cluster,min(dist1[2:41,1]))
  mins_cluster = c(mins_cluster,which.min(dist1[2:41,1]))
}


plot(pp_cluster)
ord <- rev(order(p2e_distances_cluster))
far25 <- 1:dim(randompoints)[1]
neighbors <- mins_cluster
points(randompoints, col='red', pch=4)
points(xy_cluster[mins_cluster, ], col='blue', pch=.2)

# drawing the lines, easiest via a loop
for (i in far25) 
{
  lines(rbind(xy_cluster[mins_cluster[i], ], randompoints[i, ]), col='red')
}
```



Clark and evans test
```{r}
clarkevans(ppp62)
clarkevans.test(ppp62) #0.5538762


clarkevans(ppp84)
clarkevans.test(ppp84) #0.4395466
```

Hopkins.index
```{r}
library(comato)
set.seed(123)
Hopkins.index(pairdist(ppp62)) #0.9769231
Hopkins.index(pairdist(ppp84)) #0.9420182
```



#G function
```{r}
png("gFunc62.png")
plot(Gest(ppp62), main = "G function plot")
dev.off()

png("gFunc84.png")
plot(Gest(ppp84), main = "G function plot")
dev.off()
```



#F function
```{r}
png("fFunc62.png")
plot(Fest(ppp62), main = "F function plot")
dev.off()

png("fFunc84.png")
plot(Fest(ppp84), main = "F function plot")
dev.off()
```




#K function
```{r}
K62 <- Kest(ppp62)

png("kFunc62.png")
plot(K62, main=NULL, las=1, legendargs=list(cex=0.8, xpd=TRUE, inset=c(1.01, 0) ), main = "Ripley's K function plot")
dev.off()

K84 <- Kest(ppp84)
png("kFunc84.png")
plot(K84, main=NULL, las=1, legendargs=list(cex=0.8, xpd=TRUE, inset=c(1.01, 0) ), main = "Ripley's K function plot")
dev.off()
```





#SLDA
```{r}
library(tmap)
library(spdep)
library(maptools)
library(spatialreg)
library(factoextra)
```




```{r}
?st_make_valid
cpt_areas_in_sf <- st_make_valid(cpt_areas_in_sf)


wardLevelAverages = cpt_listings_in %>%
  group_by(WARDNO) %>%
  dplyr::summarise(avePrice = mean(pclean), #price

                   #host variables
                   hsuperhost = mean(hsuperhost_TRUE),
                   aveAcceptRate = mean(na.omit(haccrclean)),

                   #types of rooms
                   aveType_enthome = mean(`rtype_Entire home/apt`),
                   aveType_Hotelroom = mean(`rtype_Hotel room`),
                   aveType_Privateroom = mean(`rtype_Private room`),
                   aveType_Sharedroom = mean(`rtype_Shared room`),

                   #accommodation specs
                   aveAccommodates =  mean(pricePH),
                   aveBedrooms = mean(na.omit(bedrooms)),
                   aveBedrooms = mean(na.omit(bathrooms)),


                   # Easy of booking variables/ availablity
                   aveInsbook =  mean(insbook_TRUE),
                   aveFbooked = mean(fbooked_TRUE),


                   #reviews
                   aveReviewScoresRating = mean(na.omit(rsr)))



tm_shape(cpt_areas_in_sf) + tm_polygons()
```


PCA
```{r}
df <- as.data.frame(wardLevelAverages[,c(-1, -4, -13)]) #Take out NA variables
df <- scale(df)
head(df)

res.pca <- prcomp(df, scale = TRUE)

png("pcaVariables.png")
fviz_pca_var(res.pca,
             col.var = "contrib", # Color by contributions to the PC
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE)
dev.off()


#Keep Sharedroom, Privateroom, aveAccomodates, avePrice, entHome and superhost
```

```{r}
cpt_areas_in_sf <- cpt_areas_in_sf %>%
separate(neighbourhood, c("Ward ","number")) %>%
  mutate(WARDNO=as.numeric(number))

#From PCA:
#Keep Sharedroom, Privateroom, aveAccomodates, avePrice, entHome and superhost bedrooms
cpt_areas_in_sf$price <- NA
cpt_areas_in_sf$t_entHome <- NA
cpt_areas_in_sf$aveType_Sharedroom <- NA
cpt_areas_in_sf$aveType_Privateroom <- NA
cpt_areas_in_sf$aveAccomodates <- NA
cpt_areas_in_sf$hsuperhost <- NA
for(j in 1:90)
{
  for(i in 1:116)
  {
    if(cpt_areas_in_sf$WARDNO[i] == wardLevelAverages$WARDNO[j])
    {
      cpt_areas_in_sf$price[i] <- wardLevelAverages$avePrice[j]
      cpt_areas_in_sf$bedrooms[i] <- wardLevelAverages$avePrice[j]
      cpt_areas_in_sf$t_entHome[i] <-wardLevelAverages$aveType_enthome[j]
      cpt_areas_in_sf$aveType_Sharedroom[i] <-wardLevelAverages$aveType_Sharedroom[j]
      cpt_areas_in_sf$aveType_Privateroom[i] <-wardLevelAverages$aveType_Privateroom[j]
      cpt_areas_in_sf$aveAccomodates[i] <-wardLevelAverages$aveAccommodates[j]
      cpt_areas_in_sf$hsuperhost[i] <-wardLevelAverages$hsuperhost[j]
    }
  }
}


cpt_areas_in_sf <-  na.omit(cpt_areas_in_sf)

png("priceObserved.png")
tm_shape(cpt_areas_in_sf) + tm_polygons(style="quantile", col = "price") +
  tm_legend(outside = TRUE, text.size = .8)
dev.off()
```

Obtain centroids
```{r}
coords <- st_coordinates(st_centroid(st_geometry(cpt_areas_in_sf)))
```


Obtain the Neighbourhood Relationship
Contiguity Based Neighbours
```{r}
#Continguincy based neighbours
#Rook style

png("rookNB.png")
nbRook <- poly2nb(as(cpt_areas_in_sf, "Spatial"), queen = FALSE) #class(nbRook)
plot(st_geometry(cpt_areas_in_sf))#nbRook[[110]]
plot(nbRook, coords, add=TRUE, col="blue")
title(main= "Rook Style neighbours")
dev.off()


#Queen style
png("queenNB.png")
nbQueen <- poly2nb(as(cpt_areas_in_sf, "Spatial"), queen = TRUE)
plot(st_geometry(cpt_areas_in_sf))
plot(nbQueen, coords, add=TRUE, col="red")
title(main= "Queen Style neighbours")
dev.off()


#differences in queen rook
png("diffNB.png")
dQueenRook <- diffnb(nbQueen, nbRook)
plot(st_geometry(cpt_areas_in_sf))
plot(nbRook, coords, add = TRUE, col = "blue")
plot(dQueenRook, coords, add = TRUE, col = "red")
title(main=paste("Differences (red) in Rook",
 "and polygon generated queen weights", sep="\n"))
dev.off()
```

Distance Based Neighbours
```{r}
#1st nearest neighbour
whoisthefirstnear=knearneigh(coords,k=1,longlat=TRUE)
knn1CPT=knn2nb(whoisthefirstnear)
png("1nnplot.png")
plot(st_geometry(cpt_areas_in_sf), main = "1st Nearest Neighbour")
plot(knn1CPT, coords, add=TRUE, col="blue")
dev.off()


#2 nearest neighbours
whois2near=knearneigh(coords,k=2,longlat=TRUE)
knn2CPT=knn2nb(whois2near)

png("2nnplot.png")
plot(st_geometry(cpt_areas_in_sf), main = "2 Nearest Neighbours")
plot(knn2CPT, coords, add=TRUE, col="blue")
dev.off()


#Critical cutoff
distBetwNeigh1=nbdists(knn1CPT,coords,longlat=TRUE)
all.linkedTresh=max(unlist(distBetwNeigh1))
all.linkedTresh


dnbTresh1=dnearneigh(coords,0,14,longlat=TRUE)
summary(dnbTresh1)

png("cutoff.png")
plot(st_geometry(cpt_areas_in_sf), main = "Cut-off")
plot(dnbTresh1, coords, add=TRUE, col="blue")
dev.off()
```

Morans I's
```{r}
nbRook.listw = nb2listw(nbRook,style ="W",zero.policy=TRUE) #cutoff
nbQueen.listw=nb2listw(nbQueen,style ="W",zero.policy=TRUE) #cutoff
knn1CPT.listw=nb2listw(knn1CPT,style ="W",zero.policy=TRUE) #cutoff
knn2CPT.listw=nb2listw(knn2CPT,style ="W",zero.policy=TRUE) #cutoff
dnbTresh1.listw=nb2listw(dnbTresh1,style ="W",zero.policy=TRUE) #cutoff


moran.test(cpt_areas_in_sf$price, nbRook.listw, zero.policy=TRUE)
moran.test(cpt_areas_in_sf$price, nbQueen.listw, zero.policy=TRUE)

moran.test(cpt_areas_in_sf$price, knn1CPT.listw, zero.policy=TRUE)
moran.test(cpt_areas_in_sf$price, knn2CPT.listw, zero.policy=TRUE)
moran.test(cpt_areas_in_sf$price, dnbTresh1.listw, zero.policy=TRUE)
```


More Moran:
```{r}
png("moranPlot.png")
moran.plot(cpt_areas_in_sf$price, nbRook.listw, zero.policy=TRUE, ylab = "Spatially lagged Price", xlab = "Price", col = 4, main = "Moran Plot")
dev.off()


Y_s = cpt_areas_in_sf$price - mean(cpt_areas_in_sf$price)
localmoranstatistics = localmoran(Y_s, nbRook.listw, zero.policy = TRUE)
head(localmoranstatistics)

cpt_areas_in_sf$localmoran <- localmoranstatistics[,1]

png("moranPricePlot.png")
tm_shape(cpt_areas_in_sf) + tm_polygons(style="quantile", col = "localmoran") +
     tm_legend(outside = TRUE, text.size = .8)
dev.off()
```



Ordinary Least Squares: Model 0
```{r}
OLScpt = lm(price ~ aveType_Privateroom + aveAccomodates, data = cpt_areas_in_sf)
summary(OLScpt)

png("olsQQ.png")
plot(OLScpt, which=2, col=c("blue"))
dev.off()

cpt_areas_in_sf$predicted <- predict(OLScpt)   # Save the predicted values
cpt_areas_in_sf$residuals <- residuals(OLScpt)

png("olsResFit.png")
plot(OLScpt, which=1, col=c("blue"))
dev.off()

plot(density(resid(OLScpt)), main="OLS Residuals", col=4)
hist(resid(OLScpt), freq=FALSE, add=TRUE, border=2)

#Global Moran
col.moran = lm.morantest(OLScpt, nbRook.listw, zero.policy = TRUE)
col.moran


png("olsPredicted.png")
tm_shape(cpt_areas_in_sf) + tm_polygons(style="quantile", col = "predicted") +
     tm_legend(outside = TRUE, text.size = .8)
dev.off()

png("olsResiduals.png")
tm_shape(cpt_areas_in_sf) + tm_polygons(style="quantile", col = "residuals") +
     tm_legend(outside = TRUE, text.size = .8)
dev.off()
```



```{r}
ST=lm.LMtests(OLScpt,listw=nbRook.listw,test="all", zero.policy = TRUE)

out=t(sapply(ST,function(x) c(x$statistic,x$parameter,x$p.value))) 

colnames(out)=c("Statistics","df","p-value")
printCoefmat(out) 

kable(out)
```



Model 1: First Order Spatial Autoregressive Model
```{r}
sarml.eigCPT1st<-lagsarlm(price ~ 1,data = cpt_areas_in_sf, 
                            listw = nbRook.listw, method = "eigen", zero.policy = TRUE)

summary(sarml.eigCPT1st)
```

Model 2: Spatial Lag Model with Independent Variables
```{r}
sarml.eigCPT<-lagsarlm(price ~ aveType_Privateroom + aveAccomodates, data = cpt_areas_in_sf, 
                            listw = nbRook.listw, method = "eigen", zero.policy = TRUE)
summary(sarml.eigCPT)


cpt_areas_in_sf$predicted <- predict(sarml.eigCPT) 
cpt_areas_in_sf$residuals <- residuals(sarml.eigCPT)

png("lagPredicted.png")
tm_shape(cpt_areas_in_sf) + tm_polygons(style="quantile", col = "predicted") +
     tm_legend(outside = TRUE, text.size = .8)
dev.off()

png("lagResiduals.png")
tm_shape(cpt_areas_in_sf) + tm_polygons(style="quantile", col = "residuals") +
     tm_legend(outside = TRUE, text.size = .8)
dev.off()


```

Model 3: Spatial Error Model
```{r}
errorsarml.eigCPT = errorsarlm(price ~ aveType_Privateroom + aveAccomodates, data = cpt_areas_in_sf,
                                    listw=nbRook.listw, method = "eigen", zero.policy = TRUE)
summary(errorsarml.eigCPT)
```

Model 4: Spatial Lag and Spatial Error model
```{r}
sacsarlm.CPT<-sacsarlm(price ~ aveType_Privateroom + aveAccomodates, data = cpt_areas_in_sf,
                           listw = nbRook.listw, zero.policy = TRUE)
summary(sacsarlm.CPT)
```



